\documentclass{resume}

\usepackage{hyperref}

\begin{document}

\name{Stéphane Travostino}
\contact{London, UK}{\href{mailto:sph@combo.cc}{sph@combo.cc}}{\href{https://github.com/1player}{github.com/1player}}

\section{TECHNICAL EXPERTISE}

\begin{itemize}
\item Fluent in C, Elixir, Go, PHP, Python and Rust software development.
\item In-depth knowledge of GNU/Linux, low-level networking, containerization and orchestration technologies such as Docker, Kubernetes and best practices to administer a modern server infrastructure: Ansible, CI/CD, GitOps, Terraform.
\item Frontend web development with Django, Phoenix, React, Javascript and TypeScript.
\end{itemize}

\section{WORK EXPERIENCE}

\datedsubsection{Combo Tech}{Senior engineering consultant}{2021--current}

\begin{itemize}
\item Development and code review of Elixir, Go, Python and Rust backend applications.
\item Consulting on architecture design, containerization, and software engineering best practices for clients worldwide.
\item Administration and maintenance of Linux servers and Kubernetes clusters.
\end{itemize}

\stack{CI/CD, Docker, Elixir, Go, Kubernetes, Linux, Python, Rust}

%

\datedsubsection{Punters Lounge}{Technical Director / Lead software engineer}{2016--2021}

\begin{itemize}
\item Modernised the entire server infrastructure with Terraform and Ansible scripts, packaged all applications into end-to-end tested containers. Eliminated single-points-of-failure with the introduction of Docker Swarm clustering, load balancers and distributed file servers.
\item Designed an Elixir backend service that ingests betting odds from multiple bookmaker APIs, and integrates them into a quasi-realtime view of the European sport and betting world. This service has been designed to be completely automated, with a web interface powered by Phoenix Live View to control and inspect its operation. The final, cleaned data is exported via GraphQL to a React/Next.js frontend website.
\item Started as a freelance PHP developer, promoted in 2018 to Technical Director to oversee the entire engineering department of the company. Helped increase revenue by 300\%, shrunk infrastructure costs by half and massively reduced technical debt.
\end{itemize}

\stack{Ansible, CI/CD, Docker, Elixir, GraphQL, Linux, MySQL, Next.js, Phoenix, PHP, PostgreSQL, React, Terraform, TypeScript}

%

\datedsubsection{GreatSway Enterprises}{C and Rust backend developer (contract)}{2015--2016}

\begin{itemize}
\item Ground-up implementation of a Rust backend application interfacing with multiple geo-distributed devices via UDP protocol. Keeps track of devices metadata and sends relevant state changes to a PHP backend.
\end{itemize}

\stack{C, Embedded development, Kubernetes, Linux, Rust}

%

\datedsubsection{Silver Spring Networks}{Full-stack Python developer (contract)}{2012--2015}

\begin{itemize}
\item Design and development of a Django web interface that aggregates and coordinates geographically distributed hardware appliances, running the ZigBee Smart Energy protocol to monitor, control, inform and automate the delivery and use of solar power generators.
\item Developed a single-page web application based on AngularJS to enable technicians to configure and keep track of the solar generators installed throughout the United States.
\end{itemize}

\stack{AngularJS, Django, Linux, Python, PostgreSQL}

%

\datedsubsection{Finiper}{Linux systems administrator (contract)}{2011--2012}

\begin{itemize}
\item Maintenance and monitoring of Oracle databases running on Solaris and RHEL systems.
\item Design of automated database reporting scripts to assist DBAs in optimising and tuning the Oracle installations.
\end{itemize}

\stack{Linux, Python, Solaris, Oracle}

%

\datedsubsection{Buongiorno}{Linux systems administrator/MySQL DBA (contract)}{2008--2011}

\begin{itemize}
\item Part of a small team of DBAs dedicated to the maintenance and performance tuning of about 150 MySQL instances.
\item Architect of a Flask web app to manage all MySQL instances through a single interface, to ease the daily workload of the database administrator by automating the management of user credentials, creation and deletions of reporting tables and presenting at a glance the status of the whole infrastructure.
\end{itemize}

\stack{Flask, Linux, Java, MySQL, Tomcat, Python}

%

\datedsubsection{General Software}{Linux systems administrator}{2006--2012}

\begin{itemize}
\item Design and ground-up development of GsView, an IT infrastructure monitoring system for Linux and Solaris inspired by Nagios and BB4.
\item PHP web development, Linux and Solaris system administration.
\end{itemize}

\stack{C, Linux, PHP, Solaris}

\end{document}
